Simulating High-Dimensional Multivariate Data

### 2020-12-17 060-conclusion-discussion.Rmd
4th draft. Address WWP ch060

We've introduced a general-purpose high-dimensional multivariate simulation algorithm and provide a high-performance `R` package called [`bigsimr`](https://schisslergroup.github.io/bigsimr/).
The random vector generation method is largely inspired by NORTA (@Cario1997) and Gaussian copula-based approaches (@MB13, @BF17, @Xia17).
The major contributions of this work are high-dimensional scaleability, flexible modeling of dependency, and an high-performance implementation with broad potential data analytic applications for modern, big-data statistical computing.

It is customary to compare new tools and algorithms directly to existing competing methods and software.
In this study, however, we only employ our proposed methodology, since our previous work has show that existing tools are simply not designed or feasible to meet our high-dimensional goal (see @Li2019gpu for evaluations of the `R` `copula`package and others). 
For the bivariate simulations, existing packages such as [`nortaRA`](https://github.com/cran/NORTARA/blob/master/inst/doc/NORTARA.R) work well to match Pearson correlations exactly.

@@

There are limitations to the methodology and implementation.
The most obvious missing feature of the proposed methodology is the inability to match a Pearson correlation matrix exactly.
As discussed in [Algorithms](algorithms) and extensively by @XZ19, this is a computationally intense procedure and Pearson's correlation is not a natural choice to describe dependency for non-normal marginals.
While we do not provide an implementation directly supporting Pearson matching, users may supply their own input Pearson correlation after using a supplementary matching scheme [@Cario1997; @XZ19].

@@

Future work includes developing scaleable algorithms to match the Pearson correlation matrix more precisely, discrete-margin specific modifications including fast Spearman's correlation rescaling (see Equation \@ref(eq:spearmanRescaled)), and high-dimensional covariance estimation.
From an implementation standpoint, `bigsimr` only supports Nvidia GPUs and redesigning the code using OpenCL would broaden the users who would benefit.
As data-analytic problems grow to even larger dimension, multi-GPU support is a promising hardware-based future direction.

>>>>

We have introduced a general-purpose high-dimensional multivariate simulation algorithm and provide a high-performance `R` package named [`bigsimr`](https://schisslergroup.github.io/bigsimr/).
The random vector generation method is largely inspired by NORTA (@Cario1997) and Gaussian copula-based approaches (@MB13, @BF17, @Xia17).
The major contributions of this work are high-dimensional scaleability, flexible modeling of dependency, and an high-performance implementation with broad potential data analytic applications for modern, big-data statistical computing.

It is customary to compare new tools and algorithms directly to existing competing methods and software.
In this study, however, we only employ our proposed methodology, as our previous work has show that existing tools are simply not designed nor feasible to meet our high-dimensional goal (see @Li2019gpu for evaluations of the `R` `copula`package and others). 
For the bivariate simulations, existing packages such as [`nortaRA`](https://github.com/cran/NORTARA/blob/master/inst/doc/NORTARA.R) work well to match Pearson correlations exactly.

@@

There are limitations to the methodology and implementation.
The most obvious missing feature of the proposed methodology is the inability to match a Pearson correlation matrix exactly.
As discussed in the [Algorithms](algorithms) section and extensively by @XZ19, this is a computationally intense procedure and Pearson's correlation is not a natural choice to describe dependency for non-normal marginals.
While we do not provide an implementation directly supporting Pearson matching, users may supply their own input Pearson correlation after employing a supplementary matching scheme [@Cario1997; @XZ19].

@@

<!-- 
Future work includes developing scaleable algorithms to match the Pearson correlation matrix more precisely, discrete-margin specific modifications including fast Spearman's correlation rescaling (see Equation \@ref(eq:spearmanRescaled)), and high-dimensional covariance estimation.
From an implementation standpoint, `bigsimr` only supports Nvidia GPUs and redesigning the code using OpenCL would broaden the users who would benefit.
As data-analytic problems grow to even larger dimension, multi-GPU support is a promising hardware-based future direction.
your comment -->
